K Nearest Neighbour Search Using Space-filling Curves

### 2013-12-07 paper/paper.tex
Figures now stay in the right place
Not sure why unit tests arent working

All methods of calculating K-Nearest Neighbours (KNN) are marred by the ``curse of dimensionality'' \cite{Bellman:2003}. Even though it is not an NP-Complete problem, it is still difficult to calculate KNN in high dimensions. Approaches such as spatially ordered trees (such as quadtrees and $kd$-trees) and space-filling curves have been applied to this problem in order to solve it more quickly than the naive approach (calculating a distance matrix between each point and choosing the smallest $k$ entries from the row corresponding to the query point $q$).

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{YeaGra.png}
\caption{Running time analysis of the Yeast dataset ($d = 8$, $n = 1484$).}
\label{run-yeast}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{ArcGra.png}
\caption{Running time analysis of the ARCENE dataset ($d = 1024$, $n = 700$).}
\label{run-arcene}
\end{center}
\end{figure}

>>>>

All methods of calculating K-Nearest Neighbours (KNN) are marred by the so-called ``curse of dimensionality'' \cite{Bellman:2003}. Even though it is not an NP-Complete problem, it is still difficult to calculate KNN in high dimensions since, if we assume that the algorithm is acting on $n$ $d$-dimensional points, the naive implementation takes $O(dn)$ time. Approaches such as spatially ordered trees (such as quadtrees and $kd$-trees) and space-filling curves have been applied to this problem in order to solve it more quickly than the naive approach (calculating a distance matrix between each point and choosing the smallest $k$ entries from the row corresponding to the query point $q$).

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{YeaGra.png}
\caption{Running time analysis of the Yeast dataset ($d = 8$, $n = 1484$).}
\label{run-yeast}
\par\vspace{\intextsep}
\includegraphics[scale=0.5]{ArcGra.png}
\caption{Running time analysis of the ARCENE dataset ($d = 1024$, $n = 700$).}
\label{run-arcene}
\end{center}
\end{figure}
